Utilizing Google's Mobility Report to predict outbreak dynamics

### 2025-02-20 products/manuscript/Manuscript.qmd
Project Work

This project explores mobility dynamics, as measured by [Google's Community Mobility Reports](https://www.google.com/covid19/mobility/), in an infectious disease context to understand and forecast disease spread. By integrating time-series infection data (provided by [Johns Hopkins University](https://github.com/CSSEGISandData/COVID-19)), the analysis aims to simulate disease outbreak scenarios and provide insights into optimal intervention strategies for mitigating future outbreaks.\
\
Google's Community Mobility Reports are anonymized insights collected from Google products, such as maps, that detail population movement trends across various categories, such as retail stores, workplaces, residencies, and more.\
\
The COVID-19 Data Repository by the Center for Systems Science and Engineering at Johns Hopkins University is a comprehensive data set that tracks global COVID-19 cases, recoveries, and deaths. It was updated regularly and compiles data from various official sources to support research.\
\
\
\

@@

@@

>>>>

This project explores mobility dynamics, as measured by [Google's Community Mobility Reports](https://www.google.com/covid19/mobility/), in an infectious disease context to understand and forecast disease spread. By integrating time-series infection data (provided by [Johns Hopkins University](https://github.com/CSSEGISandData/COVID-19)), the analysis aims to simulate disease outbreak scenarios and provide insights into optimal intervention strategies for mitigating future outbreaks. Additionally, the [County Health Ranking](https://www.countyhealthrankings.org/) is used to assess these dynamics within the context of a county's health care access and performance.\
\
Google's Community Mobility Reports are anonymized insights collected from Google products, such as maps, that detail population movement trends across various categories, such as retail stores, workplaces, residencies, and more.\
\
The COVID-19 Data Repository by the Center for Systems Science and Engineering at Johns Hopkins University is a comprehensive data set that tracks global COVID-19 cases, recoveries, and deaths. It was updated regularly and compiles data from various official sources to support research.\

The County Health Ranking is a data set that provides a comprehensive overview of various health factors and outcomes across U.S. counties. Data collected includes metrics on healthcare access, insurance coverage, income levels, violent crime, air and water quality, transportation access, and more.\
\
\

@@

How do socio-economic and health factors influence the relationship between mobility patterns and COVID-19 infection rates across U.S. counties?

Investigate if counties with similar health rankings but different mobility trends (or vice versa) experienced different outbreak severities, potentially revealing the effectiveness of local interventions \[reword\]

Examine the time lag between changes in mobility and subsequent changes in infection rates \[reword\]

@@

chr_data_2024 <- read.csv(here("data", "raw-data", "chr_trends_csv_2024.csv"))
